TITLE

### 2024-05-14 code/L1/L1_LastStep_DiversityInputObjects.Rmd
save site location keys for plants and frugivores

```{r}
# objects for functional diversity
saveRDS(PAM_plant_site_final, file = file.path(data_path_L1,"PAM_plant_site_final.rds"))
saveRDS(PAM_frugivore_site_final, file = file.path(data_path_L1,"PAM_frugivore_site_final.rds"))
saveRDS(plant_traits_df_subset, file = file.path(data_path_L1,"plant_traits_df_final.rds"))
saveRDS(frugivore_traits_df_subset, file = file.path(data_path_L1,"frugivore_traits_df_final.rds"))
```

>>>>

```{r}
# objects for functional diversity
saveRDS(site_loc_key_plant, file = file.path(data_path_L1,"site_loc_key_plant.rds"))
saveRDS(site_loc_key_frugivore, file = file.path(data_path_L1,"site_loc_key_frugivore.rds"))
saveRDS(PAM_plant_site_final, file = file.path(data_path_L1,"PAM_plant_site_final.rds"))
saveRDS(PAM_frugivore_site_final, file = file.path(data_path_L1,"PAM_frugivore_site_final.rds"))
saveRDS(plant_traits_df_subset, file = file.path(data_path_L1,"plant_traits_df_final.rds"))
saveRDS(frugivore_traits_df_subset, file = file.path(data_path_L1,"frugivore_traits_df_final.rds"))
```
